\documentclass[10pt]{moderncv}
\moderncvtheme[green]{casual}
\usepackage[utf8]{inputenc}

\usepackage[margin=0.5in]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}

\firstname{Harshal }
\familyname{Chaudhari}
\nopagenumbers{}
\newcommand{\LinkTo}[2]{\hfill \Letter \href{#1}{ \textit{#2}}}

\begin{document}
\maketitle

\section{Personal Information}
\cvline{Contact}{\email{harshal@bu.edu}{harshal@bu.edu}\ \ \ \ \ \ \ \ +1-857-294-8568}
\cvline{Website}{\href{https://www.harshalc.com}{https://www.harshalc.com}}
\cvline{Github}{\href{https://github.com/chdhr-harshal}{https://github.com/chdhr-harshal}}

\section{Research Interests}
\cvline{}{Explainable A.I. Systems, Robust Optimization, Reinforcement Learning.}

\section{Education}
\cventry{2015--2021}{Ph.D. in Computer Science}{Boston University}{}{}{Research Advisers: Prof. John Byers, Prof. Evimaria Terzi}
\cventry{2013--2015}{M.S. in Computer Science}{Boston University}{}{}{}
\cventry{2009--2013}{B.E.(Hons.) in Computer Science}{Birla Institute of Technology and Science, Pilani}{}{}{}

\section{Work Experience}
\cventry{2023--current}{Applied Scientist II}{Etsy, Boston, USA}{}{}{}
\cventry{2021--2023}{Applied Scientist I}{Etsy, Boston, USA}{}{}{}
\cventry{2018--2021}{Applied Scientist (remote, part-time)}{Zillow Group, Seattle, USA.}{}{}{}
\cventry{2018}{Applied Scientist Intern}{Zillow Group, Seattle, USA.}{}{}{}
\cventry{2015}{Data-science Intern}{Globys Inc., Seattle, USA.}{}{}{}
\cventry{2013}{Research Intern}{Siemens Corporate Research, Bangalore, India.}{}{}{}
\cventry{2011}{Software Development Intern}{KPCL, India.}{}{}{}

\section{Research Publications}
\cventry{}{Towards Flexibility and Robustness of LSM Trees}{}{}{VLDB Journal `23}{}
\cventry{}{Endure: A Robust Tuning Paradigm for LSM Trees Under Workload Uncertainty}{}{}{VLDB `22}{}
\cventry{}{Learn to Earn: Enabling Coordination Within a Ride-Hailing Fleet}{}{}{IEEE BigData `20}{}
\cventry{}{A General Framework for Fairness in Multistakeholder Recommendations}{}{}{FATREC, RecSys `20}{}
\cventry{}{Markov Chain Monitoring}{}{}{SIAM SDM `18}{}
\cventry{}{Putting Data in the Driver's Seat: Optimizing Earnings for On-Demand Ride-Hailing}{}{}{WSDM `18}{}
\cventry{}{Impacts of free app promotion: A case study on Amazon Appstore}{}{}{WCBA `17, TSMO `18}{}

\section{Professional Service}
\cvline{PC member}{WSDM, NeurIPS, KDD, WWW, SDM, etc.}
\cvline{Reviewer}{ICML, ICDE, ICWSM, etc. (Conferences), ECML-PKDD, TKDE (Journals)}

\section{Teaching Experience}
\cvline{}{Algorithmic Data Mining (Graduate), Combinatoric Structures in Discrete Mathematics, Introduction to Java Programming}

\section{Programming Experience}
\cvline{}{Python, Tensorflow, PyTorch, Apache Spark, Scala, Java, R, C/C++, SQL, etc. on GCP and AWS Cloud.}
\end{document}
